  \bib{bib:1}{article}{
    author={Baron, K.},
    title={On some orthogonally additive functions on inner product spaces},
    journal={Ann. Univ. Sci. Budapest. Sect. Comput.},
    volume={40},
    date={2013},
    pages={123--127},
  }
  \bib{bib:2}{article}{
    author={Baron, K.},
    title={Orthogonally additive bijections are additive},
    journal={Aequationes Math.},
    volume={89},
    date={2015},
    pages={297--299},
    doi={10.1007/s00010-013-0242-6},
  }
  \bib{bib:3}{article}{
    author={Baron, K.},
    title={On the continuous dependence of solutions to orthogonal additivity problem on given functions},
    journal={Ann. Math. Sil.},
    volume={29},
    date={2015},
    pages={19--23},
    doi={10.1515/amsil-2015-0002},
  }
  \bib{bib:4}{article}{
    author={Baron, K.},
    author={R\"atz, J.},
    title={On orthogonally additive mappings on inner product spaces},
    journal={Bull. Polish Acad. Sci. Math.},
    volume={43},
    date={1995},
    pages={187--189},
  }
  \bib{bib:5}{book}{
    author={Kuczma, M.},
    title={An introduction to the theory of functional equations and
      inequalities. Cauchy's equation and Jensen's inequality},
    edition={2},
    publisher={Birkh\"auser Verlag}, 
    place={Basel}, 
    date={2009},
  }
  \bib{bib:6}{article}{
    author={R\"atz, J.},
    title={On orthogonally additive mappings},
    journal={Aequationes Math.},
    volume={28},
    date={1985},
    pages={35--49},
    doi={10.1007/bf02189390},
  }
  \bib{bib:7}{book}{
    author={Sierpi\'nski, W.},
     title={Cardinal and ordinal numbers},
     series={Monografie Matematyczne},
     volume={34}, 
     publisher={Pa\'nstwowe Wydawnictwo Naukowe},
     place={Warszawa}, 
     date={1958},
   }
   \bib{bib:8}{article}{
     author={Sikorska, J.},
     title={Orthogonalities and functional equations,},
     journal={Aequationes Math.},
     volume={89},
     date={2015}, 
     pages={215--277},
     doi={10.1007/s00010-014-0288-0},
   }
