\bib{Al69}{book}{
  author={Alexiewicz, A.},
  title={Functional Analysis},
  series={Monografie Mat.},
  volume={49},
  publisher={PWN},
  place={Warszawa},
  date={1969},
  note={in Polish},
}
\bib{Ali}{book}{
  author={Aliprantis, C.},
  author={Burkinshaw, O.},
  title={Locally Solid Riesz Spaces with Applications to Economics},
  series={Mathematical Surveys and Monographs},
  volume={105},
  publisher={American Mathematical Sociaty},
  place={Providence},
  date={2003},
}
\bib{Ba}{book}{
  author={Bary, {N.\,K.}},
  title={A~Treatise on Trigonometric Series},
  volume={I, II},
  publisher={Pergamon Press},
  place={New York},
  date={1964},
}
\bib{BB}{article}{
  author={Berger, J.},
  author={Bridges, D.},
  title={A~constructive study of Landau's summability theorem},
  journal={J. UCS},
  volume={16},
  date={2010},
  number={18},
  doi={10.3217/jucs-016-18-2523},
  pages={2523--2534},
}
\bib{BO}{article}{
  author={Birnbaum, {Z.\,W.}},
  author={Orlicz, W.},
  title={\"Uber die Verallgemeinerung des Begriffes der zueinander  konjugierten Potenzen},
  journal={Studia Math.},
  volume={3},
  date={1931},
  pages={1--67},
  reprint={
    title={Władysław Orlicz. Collected Papers}, 
    publisher={PWN}, 
    place={Warszawa},
    date={1988}, 
    pages={133--199},
  },
}
\bib{Fir}{book}{
  author={Cruz-Uribe, {D.\,V.}},
  author={Fiorenza, A.},
  title={Variable Lebesgue Spaces. Foundations and Harmonic Analysis},
  publisher={Birkh\"auser},
  place={Basel},
  date={2013},
}
\bib{Die}{book}{
  author={Diening, L.},
  author={Harjulehto, P.},
  author={H\"ast\"o, P. },
  author={Ru\v zi\v cka, M.},
  title={Lebesgue and Sobolev Spaces with Variable Exponents},
  series={Lecture Notes in Math.},
  volume={2017},
  publisher={Springer},
  pplace={Berlin Heidelberg},
  date={2011},
}
\bib{HLP}{book}{
  author={Hardy, {G.\,H.}},
  author={Littlewood, {J.\,E.}},
  author={Pólya, G.},
  title={Inequalities},
  publisher={Cambridge Univ. Press},
  pplace={Cambridge},
  date={1988},
}
\bib{He}{article}{
  author={Helmberg, G.},
  title={A~construction concerning \((l^p)^{\prime} \subset l^q\)},
  journal={Amer. Math. Monthly},
  volume={111},
  date={2004},
  number={6},
  pages={518--520},
  doi={10.2307/4145070},
}
\bib{Hel}{article}{
  author={Helmberg, G.},
  title={A~Landau-type construction concerning \((L^p)^{\prime} \subset L^q\)},
  journal={Indag. Math. (N.S.)},
  volume={17},
  date={2006},
  number={2},
  doi={10.1016/S0019-3577(06)80019-4},
  pages={243--249},
}
\bib{HM}{article}{
  author={Hudzik, H.},
  author={Maligranda, L.},
  title={Amemiya norm equals Orlicz norm in general},
  journal={Indag. Math. (N.S.)},
  volume={11},
  number={4},
  date={2000},
  pages={573--585},
  doi={10.1016/s0019-3577(00)80026-9},
}
\bib{KS}{book}{
  author={Kaczmarz, S.},
  author={Steinhaus, H.},
  title={Theorie der Orthogonalreihen},
  series={Monogr. Mat.},
  volume={6},
  publisher={Warsaw},
  date={1935},
}
\bib{KK}{article}{
  author={Kamińska, A.},
  author={Kubiak, D.},
  title={The Daugavet property in the Musielak--Orlicz spaces},
  journal={J. Math. Anal. Appl.},
  volume={427},
  date={2015},
  number={2},
  pages={873--898},
  doi={10.1016/j.jmaa.2015.02.035},
}
\bib{KR91}{article}{
  author={Kov\'a{\v c}ik, O.},
  author={R\'akosn\'ik, J.},
  title={On spaces \(L^{p(x)}\)  and \(W^{k, p(x)}\)},
  journal={Czechoslovak Math. J.},
  volume={41},
  date={1991},
  number={4},
  pages={592--618},
}
\bib{Lan}{article}{
  author={Landau, E.},
  title={\"Uber einen Konvergensatz},
  journal={G\"ottingen Nachrichten},
  volume={8},
  date={1907},
  pages={25--27},
}
\bib{Ma89}{book}{
  author={Maligranda, L.},
  title={Orlicz Spaces and Interpolation},
  series={Seminars in Math.},
  volume={5},
  publisher={Univ. of Campinas},
  place={Campinas},
  date={1989},
}
\bib{Mal}{article}{
  author={Maligranda, L.},
  title={Hidegoro Nakano (1909--1974) -- on the centenary of his birth},
  book={
    title={Banach and Function  Spaces III},
    editor={Kato, M.},
    editor={Maligranda, L.},
    editor={Suzuki, T.},
    publisher={Yokohama Publishers},
    date={2011}, 
  },
  pages={99--171},
  conference={
    title={Proc. of the Third Internat. Symp. on Banach and Function Spaces (ISBFS2009)},
    date={14--17 Sept. 2009}, 
    address={Kitakyushu, Japan},
  },
}
\bib{MP}{article}{
  author={Maligranda, L.},
  author={Persson, {L.\,E.}},
  title={Generalized duality of some Banach function spaces},
  journal={Indag. Math.},
  volume={51},
  date={1989},
  number={3},
  pages={323--338},
  doi={10.1016/S1385-7258(89)80007-1},
}
\bib{MaW}{article}{
  author={Maligranda, L.},
  author={Wnuk, W.},
  title={Landau type theorem for Orlicz spaces},
  journal={Math. Z.},
  volume={208},
  date={1991},
  pages={57--64},
  doi={10.1016/s1385-7258(89)80007-1},
}
\bib{Mu76}{book}{
  author={Musielak, J.},
  title={An Introduction to Functional Analysis},
  publisher={PWN},
  place={Warszawa},
  date={1976},
  note={in Polish},
}
\bib{Mu83}{book}{
  author={Musielak, J.},
  title={Orlicz Spaces and Modular Spaces},
  series={Lecture Notes in Mathematics},
  date={1034},
  publisher={Springer-Verlag,},
  place={Berlin},
  date={1983},
}
\bib{Na50}{book}{
  author={Nakano, H.},
  title={Modulared  Semi-Ordered Linear Spaces},
  publisher={Maruzen},
  place={Tokyo},
  date={1950},
}
\bib{Na51}{book}{
  author={Nakano, H.},
  title={Topology  of Linear Topological Spaces},
  publisher={Maruzen},
  place={Tokyo},
  date={1951},
}
\bib{Orl}{article}{
  author={Orlicz, W.},
  title={\"Uber konjugierte Exponentenfolgen},
  journal={Studia Math.},
  volume={3},
  date={1931},
  pages={200--211},
  reprint={
    title={Władysław  Orlicz, Collected Papers}, 
    publisher={PWN}, 
    place={Warszawa},
    date={1988}, 
    pages={200--211},
  },
}
\bib{Sa}{article}{
  author={Samko, {S.\,G.}},
  title={Differentiation and integration of variable order and the space \(L^{p(x)}\)},
  book={
    series={Contemp. Math.},
    volume={212},
    publisher={American Mathematical Sociaty},
    place={Providence},
    date={1998},
  },
  pages={203--219},
  conference={
    title={Operator Theory for Complex and Hypercomplex Analysis}, 
    address={Mexico City}, 
    date={1994},
  },
  doi={10.1090/conm/212/02884},
}
\bib{Sh79}{article}{
  author={Sharapudinov, {I.\,I.}},
  title={The topology of the space \(\mathcal{L}^{p(t)}([0,1])\)},
  journal={Mat. Zametki},
  volume={26},
  date={1979},
  number={4},
  pages={613--632},
  note={English translation: Math. Notes 26 (1979), no. 3--4, 796--806 (1980)},
}
\bib{Sim}{article}{
  author={Simons, S.},
  title={The sequence spaces \(\ell(p_{\nu})\) and \(m(p_{\nu})\)},
  journal={Proc. London Math. Soc. (3)},
  volume={15},
  date={1965},
  pages={422--436},
  doi={10.1112/plms/s3-15.1.422},
}
\bib{ZaanII}{book}{
  author={Zaanen, A.},
  title={Riesz Spaces II},
  publisher={North-Holland},
  place={New York Oxford},
  date={1983},
}
