
  \bib{AL}{article}{
    author={Aron, {R.\,M.}},
    author={Lohman, {R.\,H.}},
    title={A~geometric function determined by extreme points of the unit ball of a~normed space},
    journal={Pacific J. Math.},
    volume={127},
    date={1987},
    pages={209--231},
  }
  \bib{ALS}{article}{
    author={Aron, {R.\,M.}},
    author={Lohman, {R.\,H.}},
    author={Su\'{a}rez Granero, A.},
    title={Rotundity, the C.S.R.P., and the \(\lambda \)-property in Banach spaces},     
    journal={Proc. Amer. Math. Soc.},
    volume={111},
    doi={10.2307/2047873},
    date={1991},
    pages={151--155},
  }
  \bib{BS}{book}{
    author={Benett, C.},
    author={Sharpley, R.},
    title={Interpolation of Operators,},
    publisher={Academic Press Inc.},
    place={London\polishendash New York\polishendash San Francisco},
    date={1988},
  }
  \bib{B}{book}{
    author={Birkhoff, G.},
    title={Lattice Theory},
    place={Providence, RI},
    date={1967},
  }
  \bib{BP}{article}{
    author={Bohonos, A.},
    author={Płuciennik, R.},
    title={\(\lambda\)-property in Orlicz spaces},
    journal={J. Convex Analysis},
    volume={21},
    number={1},
    date={2014},
    pages={147--166},
  }
  \bib{CH}{article}{
    author={Chen, {S.\,T.}},
    title={Geometry of Orlicz Spaces},
    journal={Dissertation Math.},
    volume={356},
    date={1996},
    pages={1--204},
  }
  \bib{C}{article}{
    author={Ciesielski, M.},
    title={On geometric structure of symmetric spaces},
    journal={J. Math. Anal. and Appl.},
    volume={430},
    number={1},
    doi={10.1016/j.jmaa.2015.04.040},
    date={2015},
    pages={98--125},
  }
  \bib{CKP}{article}{
    author={Ciesielski, M.},
    author={Kolwicz, P.},
    author={Płuciennik, R.},
    title={Local approach to Kadec\polishendash Klee properties in symmetric function spaces},
    journal={J. Math. Anal. and Appl.},
    volume={426},
    number={2},
    date={2015},
    doi={10.1016/j.jmaa.2015.01.064},
    pages={700--726},
  }
  \bib{CHP}{article}{
    author={Cui, {Y.\,A.}},
    author={Hudzik, H.},
    author={Płuciennik, R.},
    title={Extreme points and strongly extreme points in Orlicz spaces equipped with the Orlicz norm},
    journal={Z. Anal. Anwendungen},
    volume={22},
    doi={10.4171/ZAA/1174},
    number={4},
    title={2003},
    pages={789--817},
  }
  \bib{GKH}{article}{
    author={Grząślewicz, R.},
    author={Hudzik, H.},
    author={Kurc, W.},
    title={Extreme and exposed points in Orlicz spaces},
    journal={Canad. J. Math},
    volume={44},
    doi={10.4153/CJM-1992-032-3},
    number={3},
    date={1992},
    pages={505--515},
  }
  \bib{HKM-s}{article}{
    author={Hudzik, H.},
    author={Kamińska, A.},
    author={Mastyło, M.},
    title={Monotonicity and rotundity properties in Banach lattices},
    journal={Rocky Mountain J. Math.},
    volume={30},
    number={3},
    date={2000},
    pages={933--949},
    doi={10.1216/rmjm/1021477253},
  }
  \bib{KPS}{book}{
    author={Krein, {S.\,G.}},
    author={Petunin, {Ju.\,I.}},
    author={Semenov, {E.\,M.}},
    title={Interpolation of Linear Operators},
    series={AMS Trans. of Math. Monographs},
    volume={54},
    place={Providence, {R.\,I.}},
    date={1982},
  }
  \bib{L}{article}{
    author={Lohman, {R.\,H.}},
    title={The \(\lambda \)-function in Banach spaces},
    book={
      title={Banach Space Theory}, 
      series={Contemp. Math.}, 
      volume={85}, 
      publisher={Amer. Math. Soc.}, 
      place={Providence, R.I.}, 
      date={1989}, 
    },
      pages={345--351},
  }
  \bib{M}{book}{
    author={Musielak, J.},
    title={Orlicz Spaces and Modular Spaces},
    series={Lecture Notes in Math.},
    volume={1034},
    publisher={Springer\dywiz Verlag},
    date={1983},
    pages={1--222},
  }
