
  \bib{BS}{book}{
    author={Bennet, C.},
    author={Sharpley, R.},
    title={Interpolation of
      Operators},
    publisher={Academic Press},
    place={Boston},
    date={1988},
  }
  \bib{BL}{book}{
    author={Bergh, J.},
    author={L\"{o}fstr\"{o}m, J.},
    title={Interpolation Spaces. An Introduction},
    publisher={Springer},
    place={Berlin},
    date={1976},
  }
  \bib{BK}{book}{
    author={Brudnyi, {Yu.\,A.}},
    author={Krugljak, {N.\,Ya.}},
    title={Interpolation Functors and Interpolation
      Spaces},
    volume={1},
    publisher={North-Holland}, 
    place={Amsterdam}, 
    date={1991},
  }
  \bib{BB}{book}{
    author={Butzer, P.L.},
    author={Berens, H.},
    title={Semi-Groups of Operators and
      Approximation},
    publisher={Springer},
    place={New York},
    date={1967},
  }
  \bib{CFKU}{article}{
    author={Cobos, F.},
    author={Fern\'{a}ndez-Cabrera, {L.\,M.}},
    author={K\"{u}hn, T. },
    author={Ullrich, T.},
    title={On an extreme class of real interpolation spaces},
    journal={J. Funct. Anal.},
    volume={256},
    doi={10.1016/j.jfa.2008.12.013},
    date={2009},
    pages={2321--2366},
  }
  \bib{CFM}{article}{
    author={Cobos, F.},
    author={Fern\'{a}ndez-Cabrera, {L.\,M.}},
    author={Masty{\l}o, M.},
    title={Abstract limit \(J\)-spaces},
    journal={J. London Math. Soc.},
    volume={82},
    doi={10.1112/jlms/jdq043},
    date={2010},
    pages={501--525},
  }
  \bib{CK}{article}{
    author={Cobos, F.},
    author={K\"{u}hn, T.},
    title={Extrapolation estimates for entropy numbers},
    journal={J. Funct. Anal.},
    volume={263},
    date={2012},
    doi={10.1016/j.jfa.2012.09.016},
    pages={4009--4033},
  }
  \bib{FK}{article}{
    author={Fiorenza, A.},
    author={Karadzhov, {G.\,E.}},
    title={Grand and small Lebesgue spaces and their analogs},
    journal={Z. Anal. Anwendungen},
    volume={23},
    date={2004},
    pages={657--681},
    doi={10.4171/zaa/1215},
  }
  \bib{JM}{book}{
    author={Jawerth, B.},
    author={Milman, M.},
    title={Extrapolation theory with applications},
    series={Mem. Amer. Math. Soc.},
    volume={440},
    date={1991},
  }
  \bib{KM}{article}{
    author={Karadzhov, {G.\,E.}},
    author={Milman, M.},
    title={Extrapolation theory: new results and applications},
    journal={J. Approx. Theory},
    volume={133},
    date={2005},
    pages={38--99},
    doi={10.1016/j.jat.2004.12.003},
  }
  \bib{Kt}{book}{
    author={K{\"o}the, G.},
    title={Topological Vector Spaces I},
    publisher={Springer},
    place={Berlin},
    date={1969},
  }
  \bib{Kg}{book}{
    author={K{\"o}nig, H.},
        title={Eigenvalue Distributions of Compact Operators},
    publisher={Birkh{\"a}user},
    place={Basel},
    date={1986},
  }
  \bib{M}{article}{
    author={Milman, M.},
    title={A~note on extrapolation theory},
    journal={J. Math. Anal. Appl.},
    volume={282},
    date={2003},
    pages={26--47},
    doi={10.1016/s0022-247x(03)00182-3},
  }
  \bib{N}{article}{
    author={Nilsson, P.},
    title={Reiteration theorems for real interpolation and approximation spaces},
    journal={Ann. Mat. Pura Appl.},
    volume={132},
    date={1982},
    pages={291--330},
  }
  \bib{T}{book}{
    author={Triebel, H.},
    title={Interpolation Theory, Function Spaces, Differential
      Operators},
    publisher={North-Holland},
    place={Amsterdam},
    date={1978},
  }
  \bib{T2}{book}{
    author={Triebel, H.},
    title={Theory of Function
      Spaces II},
    publisher={Birkh\"auser},
    place={Basel},
    date={1992},
  }
